### 2018-07-28 Sections/quality_of_service.tex
minor
dB, \text->mathrm

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob. Let us assume a bit-flip error model in this instance\footnote{The same protocol can be employed to correct against phase-flip errors by operating in a Hadamard-rotated basis.}, in which case the imperfect Bell pairs are of the form,
\begin{align}
\hat\rho^F_{A,B} &= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\hat{X}_1\ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \nonumber \\
&= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\ket{\Psi^+}\bra{\Psi^+},
\end{align}
That is, we have a mixture of,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B + \ket{1}_A\ket{1}_B),	
\end{align}
with probability $F$, and,
\begin{align}
\ket{\Psi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B + \ket{1}_A\ket{0}_B),	
\end{align}
with probability \mbox{$1-F$}. The goal is to `filter' out the latter of these.
x 
Alice and Bob then perform their entanglement purification protocol -- operations to reduce them to a single Bell pair of higher fidelity,
\begin{align}
\mathcal{E}_\text{purif}(\hat\rho^{F_\text{in}}_{A,B} \otimes \hat\rho^{F_\text{in}}_{A,B}) \to \hat\rho^{F_\text{out}}_{A,B},
\end{align}
where,
\begin{align}
F_\text{out}>F_\text{in}.
\end{align}

The purification process $\mathcal{E}_\text{purif}$ is realised very simply by Alice and Bob both performing parity measurements\index{Bell measurement} on their two qubits, whose measurement outcomes indicate whether the two qubits were equal ($+$) or different ($-$) -- their parity. These are easily implemented using CNOT gates, using the construction shown in Fig.~\ref{fig:parity_meas}, which implement the projectors,
\begin{align}\index{Parity measurement}\index{Parity projectors}
\hat\Pi^+ &= \ket{0,0}\bra{0,0} + \ket{1,1}\bra{1,1}, \nonumber \\
\hat\Pi^- &= \ket{0,1}\bra{0,1} + \ket{1,0}\bra{1,0}.
\end{align}

@@

\subsubsection{Operation of protocol}

@@

Suppose there were no errors, the ideal case. Then the input state was,
\begin{align}
\ket\psi_\text{in} &= \ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4}\\
&= \frac{1}{2}(\ket{0}_1\ket{0}_2+\ket{1}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Upon parity measurement we obtain,
\begin{align}
\hat\Pi^+_{1,3} \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},\nonumber \\
\hat\Pi^-_{1,3} \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},
\end{align}
and we obtain the desired output Bell-pair (with an $\hat{X}$ correction in the case of the odd-parity outcome).

@@

Now suppose there was a bit-flip error on the first qubit of the first pair. Now the input state is,
\begin{align}
\ket\psi_\text{in} &= \hat{X}_1 \ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4}\\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Now upon parity measurement we obtain,
\begin{align}
\hat\Pi^+_{1,3} \hat{X}_1\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},\nonumber \\
\hat\Pi^-_{1,3} \hat{X}_1\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},
\end{align}
and following correction we achieve a bit-flipped Bell-pair.

Finally, with both Bell-pairs subject to a single bit-flip,
\begin{align}
\ket\psi_\text{in} &= \hat{X}_1\hat{X}_3 \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} \\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{1}_3\ket{0}_4+\ket{0}_3\ket{1}_4).\nonumber
\end{align}
Upon performing the parity measurement,
\begin{align}
\hat\Pi^+_{1,3} \hat{X}_1\hat{X}_3\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},\nonumber \\
\hat\Pi^-_{1,3} \hat{X}_1\hat{X}_3\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},
\end{align}
recovering the expected Bell-pair, without an erroneous bit-flip.

Evidently, the output Bell-pair is subject to an unexpected bit-flip iff one of the Bell-pairs was subject to a bit-flip error. This yields the output fidelity,
\begin{align}
F_\mathrm{out} = \frac{{F_\mathrm{in}}^2}{{F_\mathrm{in}}^2 + (1-F_\mathrm{in})^2},
\end{align}
and thus the purification protocol improves fidelity provided that \mbox{$F_\mathrm{in}>1/2$}.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ThreeQubitCode($\ket\psi$):
\begin{enumerate}
\item Using two CNOT gates, redundantly encode the logical single-qubit state,
\begin{align}
\ket\psi=\alpha\ket{0}+\beta\ket{1},
\end{align}
into the 3-qubit state,
\begin{align}
\ket\psi_R &= \hat{\text{CNOT}}_{1,2}\hat{\text{CNOT}}_{1,3}\ket\psi\ket{00} \nonumber \\
&= \alpha\ket{000}+\beta\ket{111}.
\end{align}
\item Independently apply bit-flip channels $\mathcal{E}_X$ to each of the three encoded qubits.
\item If exactly one bit-flip operation was applied in total, the three possible erroneous encoded states are,
\begin{align}
\ket\psi_1 &= \hat{X}_1 \ket\psi_R = \alpha\ket{001}+\beta\ket{110}, \nonumber \\
\ket\psi_2 &= \hat{X}_2 \ket\psi_R = \alpha\ket{010}+\beta\ket{101}, \nonumber \\
\ket\psi_3 &= \hat{X}_3 \ket\psi_R = \alpha\ket{100}+\beta\ket{011}.
\end{align}
\item Determine the parity of each of the three pairs of encoded qubits.
\item Assuming at most a single bit-flip operation has occurred on the encoded state, the three parity outcomes uniquely determine which encoded qubit the bit-flip was applied to.
\item Apply classically-controlled bit-flip recovery operations, $\mathcal{R}$, to correct the encoded state, recovering $\ket\psi_R$.
\item Apply the inverse of the encoding operation to recover $\ket\psi$.
\item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1.3em @R=.6em {
  & \lstick{\ket{\psi}} & \ctrl{2} & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{3}  & \qw       & \ctrl{4} & \qw & \multigate{2}{\ \mathcal{R}\ } & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{2}  & \ctrl{2}  & \qw      & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \qw       & \ctrl{2}  & \ctrl{3} & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  &          &          &          & & \lstick{\ket{0}} & \targ \qw & \qw       & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \targ \qw & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \qw       & \targ    & \meter & \control \cw \cwx
} \nonumber
\end{align}
\end{mdframed}
\caption{3-qubit code for protecting against at most a single logical bit-flip error. The doubly-controlled CNOT gates represent parity measurements, \mbox{$n_3=n_1\oplus n_2$}, where $n_i$ represents the value of the $i$th qubit. In a Hadamard-rotated basis, the same circuit may be employed to protect against a single phase-flip error. And by concatenating the two we obtain a 9-qubit code protecting against a single depolarising error (i.e joint bit-flip/phase-flip), which is a universal single-qubit error model.} \label{alg:three_QEC}
\end{table}

@@

The most common topological code, which we will use here as an example, is the toric code\index{Toric code}, which resides on a lattice graph over the surface of a torus\footnote{As with cluster states, this graph needn't (but could) correspond to a network graph.}. As with cluster states (Sec.~\ref{sec:CSQC}), the toric code is most easily visualised in the stabiliser formalism\index{Stabiliser formalism}, and the toric code is an example of a stabiliser code\index{Stabiliser code} (Sec.~\ref{sec:stab_code}). Consider a rectangular sub-graph of the torus. We place a qubit on each edge (not vertex) of the graph. Now we define two sets of stabiliser operators: \textit{star} ($\hat{S}_+$) and \textit{plaquette} ($\hat{S}_\square$) operators,
\begin{align} \index{Surface code stabilisers}\index{Star operator}\index{Plaquette operator}
	\hat{S}_+(v) &= \prod_{i\in e(v)} \hat{X}_i, \nonumber \\
	\hat{S}_\square(p) &= \prod_{i\in e(p)} \hat{Z}_i,
\end{align}
where $e(v)$ are the edges neighbouring vertex $v$, and $e(p)$ are the edges surrounding plaquette $p$. By definition, the toric code state, $\ket\psi_\text{toric}$, satisfies the stabiliser relations,
\begin{align}
	\hat{S}_+(v) \ket\psi_\text{toric} &= \ket\psi_\text{toric} \,\forall\, v, \nonumber \\
	\hat{S}_\square(p) \ket\psi_\text{toric} &= \ket\psi_\text{toric} \,\forall\, p.
\end{align}
The stabilisers can be visualised graphically as per Fig.~\ref{fig:toric_code}.

@@

Suppose we desire to implement some linear optics unitary network, $\hat{U}_\text{target}$, but our fabrication techniques are imperfect and we instead implement a close approximation to it. How can we overcome this?

\cite{MarshmanLundRohdeRalph} showed that by using an optical fanout operation, which splits a set of optical modes equally across multiple sets of modes in a type of redundant encoding, and passing each set through an independently manufactured copy of the imperfect unitary, $\tilde{U}_i$, upon post-selection on detecting all photons in the desired output modes, the output state will behave as if it had evolved through a network given by the arithmetic average of each of the imperfect copies of $\hat{U}_\text{target}$,
\begin{align}
\hat{U}_\text{av} = \frac{1}{M}\sum_{i=1}^M \tilde{U}_i.	
\end{align}
A schematic for the optical circuit is shown in Fig.~\ref{fig:error_av_circuit}.

@@

The protocol is necessarily non-deterministic, since sometimes photons will be measured in the error modes, signalling that the output state has been projected onto an erroneous subspace. However, when post-selection succeeds we have effectively evolved via the averaged operator, which statistically ought to more closely approximate $\hat{U}_\text{target}$ than the individual $\tilde{U}_i$.

@@

An alternate mechanism by which errors could be introduced into our system is via coupling to an external environment (for example via an electromagnetic field) introducing a persistent evolution of our qubits, which is slow-moving compared to the rate at which the implemented computation is evolving the system. We can model this as a joint system/environment Hamiltonian of the form,
\begin{align}\label{eq:dyn_dec_ham}
\hat{H}_\text{total} = \lambda_\text{comp}\hat{H}_\text{comp} + \lambda_\text{env}\hat{H}_\text{env} + \lambda_\text{int}\hat{H}_\text{int},	
\end{align}
where the different components represent, in order, the Hamiltonians of the: total joint system; quantum computer (or system of interest); environment; interaction between system and environment. We are specifically operating in the regime where \mbox{$\lambda_\text{int}\ll\lambda_\text{comp}$}, such that the computation is the dominant term in the evolution and the environmental coupling can be treated as a small perturbation from the desired evolution.

The goal of dynamical decoupling is to minimise the influence of the system/environment interaction term, $\hat{H}_\text{int}$, by manipulating the system in such a way that this term continuously cancels itself out over time.

@@

Now if we proceed for two time-steps, once bit-flipped and another not, we have,
\begin{align}
\underbrace{\hat{Z}(\theta)}_{\text{forward}}\cdot\underbrace{[\hat{X}\hat{Z}(\theta)\hat{X}]}_{\text{reverse}} = \hat{\mathbb{I}},
\end{align}
and the unknown phase-rotation has been eliminated. The sequence is illustrated on the Bloch sphere\index{Bloch sphere} in Fig.~\ref{fig:bloch_sphere_dyn_dec}.

@@

As described above, we have merely error corrected a quantum memory. Of course we wish to implement far more sophisticated evolutions. This requires breaking down the computational evolution (given by $\hat{H}_\text{comp}$) into a large number of small, discrete steps. These are interspersed with our bang-bang control sequence so as to continuously remove any phase-errors accumulated during the course of the computation.

>>>>

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob. Let us assume a bit-flip error model in this instance\footnote{The same protocol can be employed to correct against phase-flip errors by operating in a Hadamard-rotated basis.}, in which case the imperfect Bell pairs are of the form,
\begin{align}
\hat\rho^F_{A,B} &= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\hat{X}_1\ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \nonumber \\
&= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\ket{\Psi^+}\bra{\Psi^+},
\end{align}
That is, we have a mixture of,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B + \ket{1}_A\ket{1}_B),	
\end{align}
with probability $F$, and,
\begin{align}
\ket{\Psi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B + \ket{1}_A\ket{0}_B),	
\end{align}
with probability \mbox{$1-F$}. The goal is to `filter' out the latter of these.
x 
Alice and Bob then perform their entanglement purification protocol -- operations to reduce them to a single Bell pair of higher fidelity,
\begin{align}
\mathcal{E}_\mathrm{purif}(\hat\rho^{F_\mathrm{in}}_{A,B} \otimes \hat\rho^{F_\mathrm{in}}_{A,B}) \to \hat\rho^{F_\mathrm{out}}_{A,B},
\end{align}
where,
\begin{align}
F_\mathrm{out}>F_\mathrm{in}.
\end{align}

The purification process $\mathcal{E}_\mathrm{purif}$ is realised very simply by Alice and Bob both performing parity measurements\index{Bell measurement} on their two qubits, whose measurement outcomes indicate whether the two qubits were equal ($+$) or different ($-$) -- their parity. These are easily implemented using CNOT gates, using the construction shown in Fig.~\ref{fig:parity_meas}, which implement the projectors,
\begin{align}\index{Parity measurement}\index{Parity projectors}
\hat\Pi^+ &= \ket{0,0}\bra{0,0} + \ket{1,1}\bra{1,1}, \nonumber \\
\hat\Pi^- &= \ket{0,1}\bra{0,1} + \ket{1,0}\bra{1,0}.
\end{align}

@@

@@

Suppose there were no errors, the ideal case. Then the input state was,
\begin{align}
\ket\psi_\mathrm{in} &= \ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4}\\
&= \frac{1}{2}(\ket{0}_1\ket{0}_2+\ket{1}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Upon parity measurement we obtain,
\begin{align}
\hat\Pi^+_{1,3} \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},\nonumber \\
\hat\Pi^-_{1,3} \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},
\end{align}
and we obtain the desired output Bell-pair (with an $\hat{X}$ correction in the case of the odd-parity outcome).

@@

Now suppose there was a bit-flip error on the first qubit of the first pair. Now the input state is,
\begin{align}
\ket\psi_\mathrm{in} &= \hat{X}_1 \ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4}\\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Now upon parity measurement we obtain,
\begin{align}
\hat\Pi^+_{1,3} \hat{X}_1\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},\nonumber \\
\hat\Pi^-_{1,3} \hat{X}_1\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},
\end{align}
and following correction we achieve a bit-flipped Bell-pair.

Finally, with both Bell-pairs subject to a single bit-flip,
\begin{align}
\ket\psi_\mathrm{in} &= \hat{X}_1\hat{X}_3 \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} \\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{1}_3\ket{0}_4+\ket{0}_3\ket{1}_4).\nonumber
\end{align}
Upon performing the parity measurement,
\begin{align}
\hat\Pi^+_{1,3} \hat{X}_1\hat{X}_3\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},\nonumber \\
\hat\Pi^-_{1,3} \hat{X}_1\hat{X}_3\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},
\end{align}
recovering the expected Bell-pair, without an erroneous bit-flip.

Evidently, the output Bell-pair is subject to an unexpected bit-flip iff one of the Bell-pairs was subject to a bit-flip error. This yields the output fidelity,
\begin{align}
F_\mathrm{out} = \frac{{F_\mathrm{in}}^2}{{F_\mathrm{in}}^2 + (1-F_\mathrm{in})^2},
\end{align}
and thus the purification protocol improves fidelity provided that \mbox{$F_\mathrm{out}>F_\mathrm{in}$}, which implies the input fidelity must satisfy \mbox{$F_\mathrm{in}>1/2$}.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ThreeQubitCode($\ket\psi$):
\begin{enumerate}
\item Using two CNOT gates, redundantly encode the logical single-qubit state,
\begin{align}
\ket\psi=\alpha\ket{0}+\beta\ket{1},
\end{align}
into the 3-qubit state,
\begin{align}
\ket\psi_R &= \hat{\mathrm{CNOT}}_{1,2}\hat{\mathrm{CNOT}}_{1,3}\ket\psi\ket{00} \nonumber \\
&= \alpha\ket{000}+\beta\ket{111}.
\end{align}
\item Independently apply bit-flip channels $\mathcal{E}_X$ to each of the three encoded qubits.
\item If exactly one bit-flip operation was applied in total, the three possible erroneous encoded states are,
\begin{align}
\ket\psi_1 &= \hat{X}_1 \ket\psi_R = \alpha\ket{001}+\beta\ket{110}, \nonumber \\
\ket\psi_2 &= \hat{X}_2 \ket\psi_R = \alpha\ket{010}+\beta\ket{101}, \nonumber \\
\ket\psi_3 &= \hat{X}_3 \ket\psi_R = \alpha\ket{100}+\beta\ket{011}.
\end{align}
\item Determine the parity of each of the three pairs of encoded qubits.
\item Assuming at most a single bit-flip operation has occurred on the encoded state, the three parity outcomes uniquely determine which encoded qubit the bit-flip was applied to.
\item Apply classically-controlled bit-flip recovery operations, $\mathcal{R}$, to correct the encoded state, recovering $\ket\psi_R$.
\item Apply the inverse of the encoding operation to recover $\ket\psi$.
\item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1.3em @R=.6em {
  & \lstick{\ket{\psi}} & \ctrl{2} & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{3}  & \qw       & \ctrl{4} & \qw & \multigate{2}{\ \mathcal{R}\ } & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{2}  & \ctrl{2}  & \qw      & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \qw       & \ctrl{2}  & \ctrl{3} & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  &          &          &          & & \lstick{\ket{0}} & \targ \qw & \qw       & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \targ \qw & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \qw       & \targ    & \meter & \control \cw \cwx
} \nonumber
\end{align}
\end{mdframed}
\caption{3-qubit code for protecting against at most a single logical bit-flip error. The doubly-controlled CNOT gates represent parity measurements, \mbox{$n_3=n_1\oplus n_2$}, where $n_i$ represents the value of the $i$th qubit. In a Hadamard-rotated basis, the same circuit may be employed to protect against a single phase-flip error. And by concatenating the two we obtain a 9-qubit code protecting against a single depolarising error (i.e joint bit-flip/phase-flip), which is a universal single-qubit error model.} \label{alg:three_QEC}
\end{table}

@@

The most common topological code, which we will use here as an example, is the toric code\index{Toric code}, which resides on a lattice graph over the surface of a torus\footnote{As with cluster states, this graph needn't (but could) correspond to a network graph.}. As with cluster states (Sec.~\ref{sec:CSQC}), the toric code is most easily visualised in the stabiliser formalism\index{Stabiliser formalism}, and the toric code is an example of a stabiliser code\index{Stabiliser code} (Sec.~\ref{sec:stab_code}). Consider a rectangular sub-graph of the torus. We place a qubit on each edge (not vertex) of the graph. Now we define two sets of stabiliser operators: \textit{star} ($\hat{S}_+$) and \textit{plaquette} ($\hat{S}_\square$) operators,
\begin{align} \index{Surface code stabilisers}\index{Star operator}\index{Plaquette operator}
	\hat{S}_+(v) &= \prod_{i\in e(v)} \hat{X}_i, \nonumber \\
	\hat{S}_\square(p) &= \prod_{i\in e(p)} \hat{Z}_i,
\end{align}
where $e(v)$ are the edges neighbouring vertex $v$, and $e(p)$ are the edges surrounding plaquette $p$. By definition, the toric code state, $\ket\psi_\mathrm{toric}$, satisfies the stabiliser relations,
\begin{align}
	\hat{S}_+(v) \ket\psi_\mathrm{toric} &= \ket\psi_\mathrm{toric} \,\forall\, v, \nonumber \\
	\hat{S}_\square(p) \ket\psi_\mathrm{toric} &= \ket\psi_\mathrm{toric} \,\forall\, p.
\end{align}
The stabilisers can be visualised graphically as per Fig.~\ref{fig:toric_code}.

@@

Suppose we desire to implement some linear optics unitary network, $\hat{U}_\mathrm{target}$, but our fabrication techniques are imperfect and we instead implement a close approximation to it. How can we overcome this?

\cite{MarshmanLundRohdeRalph} showed that by using an optical fanout operation, which splits a set of optical modes equally across multiple sets of modes in a type of redundant encoding, and passing each set through an independently manufactured copy of the imperfect unitary, $\tilde{U}_i$, upon post-selection on detecting all photons in the desired output modes, the output state will behave as if it had evolved through a network given by the arithmetic average of each of the imperfect copies of $\hat{U}_\mathrm{target}$,
\begin{align}
\hat{U}_\mathrm{av} = \frac{1}{M}\sum_{i=1}^M \tilde{U}_i.	
\end{align}
A schematic for the optical circuit is shown in Fig.~\ref{fig:error_av_circuit}.

@@

The protocol is necessarily non-deterministic, since sometimes photons will be measured in the error modes, signalling that the output state has been projected onto an erroneous subspace. However, when post-selection succeeds we have effectively evolved via the averaged operator, which statistically ought to more closely approximate $\hat{U}_\mathrm{target}$ than the individual $\tilde{U}_i$.

@@

An alternate mechanism by which errors could be introduced into our system is via coupling to an external environment (for example via an electromagnetic field) introducing a persistent evolution of our qubits, which is slow-moving compared to the rate at which the implemented computation is evolving the system. We can model this as a joint system/environment Hamiltonian of the form,
\begin{align}\label{eq:dyn_dec_ham}
\hat{H}_\mathrm{total} = \lambda_\mathrm{comp}\hat{H}_\mathrm{comp} + \lambda_\mathrm{env}\hat{H}_\mathrm{env} + \lambda_\mathrm{int}\hat{H}_\mathrm{int},	
\end{align}
where the different components represent, in order, the Hamiltonians of the: total joint system; quantum computer (or system of interest); environment; interaction between system and environment. We are specifically operating in the regime where \mbox{$\lambda_\mathrm{int}\ll\lambda_\mathrm{comp}$}, such that the computation is the dominant term in the evolution and the environmental coupling can be treated as a small perturbation from the desired evolution.

The goal of dynamical decoupling is to minimise the influence of the system/environment interaction term, $\hat{H}_\mathrm{int}$, by manipulating the system in such a way that this term continuously cancels itself out over time.

@@

Now if we proceed for two time-steps, once bit-flipped and another not, we have,
\begin{align}
\underbrace{\hat{Z}(\theta)}_{\mathrm{forward}}\cdot\underbrace{[\hat{X}\hat{Z}(\theta)\hat{X}]}_{\mathrm{reverse}} = \hat{\mathbb{I}},
\end{align}
and the unknown phase-rotation has been eliminated. The sequence is illustrated on the Bloch sphere\index{Bloch sphere} in Fig.~\ref{fig:bloch_sphere_dyn_dec}.

@@

As described above, we have merely error corrected a quantum memory. Of course we wish to implement far more sophisticated evolutions. This requires breaking down the computational evolution (given by $\hat{H}_\mathrm{comp}$) into a large number of small, discrete steps. These are interspersed with our bang-bang control sequence so as to continuously remove any phase-errors accumulated during the course of the computation.
